---
title: "Full Code"
output: html_document
date: "2025-08-01"
---

```{r}
library(tidyverse)
library(hockeyR)
library(vetiver)

app <- VetiverAPI(v, check_prototype = TRUE)

pbp_2021 <- load_pbp("2020-2021")
pbp_2122 <- load_pbp("2021-2022")
pbp_2223 <- load_pbp("2022-2023")
pbp_2324 <- load_pbp("2023-2024")

pbp_2021_1 <- pbp_2021 |>
  select(event_type, secondary_type, strength_state, x, y, shot_distance, shot_angle) |>
  filter(event_type == "SHOT" | event_type == "BLOCKED_SHOT" |
           event_type == "MISSED_SHOT" | event_type == "GOAL") |>
  filter(strength_state == "5v5") |>
   mutate(
     is_goal = ifelse(event_type == "GOAL",1,0))

a <- glm(is_goal ~ as.factor(secondary_type) + shot_distance + shot_angle, family = binomial, data = pbp_2021_1)


summary(a)


```

```{r}
library(vetiver)
v <- vetiver_model(rf_fit, "sacramento_rf") # this is fitting it with vetiver




```

log on with the .pem key:

ssh -i .pem name \

# chapter 8 lab

• Multiple levels of logging for user interactions and external API calls within the shiny

-   ch 4, understanding log levels

# all of this goes in your docker file?

library(vetiver) library(plumber) \# vetiver_model \<- vetivermodel(a, "name") when you get a to work vetiver_api(vetiver_model) \|\> pr_run(port = 8000)

vetiver_prepare_docker( board, \# here it should be a remote file .... ) \# deploy with docker in MLOps with vetiver book

### for each game, we can get expected goals per player?

upload docker file into EC2 instance.

docker file is created locally, but need some credentials to add it into your EC2 instance (SSH/SEP file copy)
